### 2020-04-03 poster/src/poster.tex
Poster

\begin{columns}[t]
  \begin{column}{0.900\linewidth}
  \begin{block}{\Large Graph Streams \& The $\mathtt{Neighbourhood\ Detection\ Problem}$}
 	\noindent
	Graph Streams are a sequence of instructions which describe how to construct a graph. Each instruction provides details about an edge in the graph. Graph Streams come in two forms
	\begin{itemize}
		\item Instructions in an \textit{Insertion-Only Streams} only ever insert new edges into the graph.
		\item Instructions in an \textit{Insertion-Deletion Streams} either insert a new edge, or remove an existing edge, from the graph.
	\end{itemize}
	In the $\mathtt{Neighbourhood\ Detection\ Problem}(n,d)$ we are given a graph with $n$ vertices \& at least one vertex of degree $d$. We are tasked to return a vertex with at least $\frac{d}c$ of its neighbours, from some approximation factor $c\geq1$.\\
	\noindent
	There are some good motivativing applications of the $\mathtt{Neighbourhood\ Detection\ Problem}$.
	\begin{itemize}
		\item Given a network of social media connections detect popular influencers and analyse the demographics they attract in order to plan targetted advertising campaigns.
		\item Given a log of traffic to a network detect whether a DDOS attack has occurred and, if so, by whom.
		\item Given a list of sales made on a website detect which items are most popular and which items they are commonly bought with.
	\end{itemize}
  \end{block}
  \end{column}
\end{columns}

>>>>

\begin{columns}[t]
  \begin{column}{0.900\linewidth}
  \begin{block}{\Large Graph Streams \& The $\mathtt{Neighbourhood\ Detection\ Problem}$}
 	\noindent
	Graph Streams are a sequence of instructions which describe how to construct a graph. Each instruction provides details about an edge in the graph. Graph Streams come in two forms
	\begin{itemize}
		\item \textit{Insertion-Only Streams} only ever insert new edges into the graph with each instruction.
		\item \textit{Insertion-Deletion Streams} either insert a new edge, or remove an existing edge, from the graph with each instruction.
	\end{itemize}
	In the $\mathtt{Neighbourhood\ Detection\ Problem}(n,d)$ we are given a graph with $n$ vertices \& at least one vertex of degree $d$. We are tasked to return a vertex with at least $\frac{d}c$ of its neighbours, from some approximation factor $c\geq1$.\\
	\noindent
	There are some good motivativing applications of the $\mathtt{Neighbourhood\ Detection\ Problem}$.
	\begin{itemize}
		\item Given a network of social media accounts, detect popular influencers and analyse the demographics they attract in order to plan targetted advertising campaigns.
		\item Given a log of traffic to a network detect whether a DDOS attack has occurred and, if so, by whom.
		\item Given a list of sales made on a website detect which items are most popular and which items they are commonly bought with.
	\end{itemize}
  \end{block}
  \end{column}
\end{columns}
